---
title: "social_media_NP_data_exploration"
author: "Logan Hysen"
date: "2024-07-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Import packages
library(dplyr)
library(readxl)
library(ggplot2)
library(tidyr)
```

Let's define a function that will take our input data and then format it so we can plot it more easily
```{r}

```


Read our sentiment data in
```{r}
dat <- read_excel("C:/Users/logan/Desktop/social_media_NP/data/National_Parks_with_topics_sentiment (1).xlsx", 
                  sheet = 1)

dat <- filter(dat, sentiment_confidence >=.50)
dat <- group_by(dat, NP)


```


Calculate the mean sentiment for each National Park
```{r}
parkAvgs <- summarise(dat, avg = mean(overall_sentiment))

print(parkAvgs)
```

```{r, message = TRUE, include = TRUE, fig.cap="Average NP visitation"}

ggplot(parkAvgs, aes(y = avg, x = NP)) +
  geom_point() +
  lims(y = c(3,5)) +
  theme(axis.text.x = element_text(size = 10, angle = 60, vjust = 1, hjust=1))

```

Let's calculate how many visitors left reviews from each country by NP

```{r}
dat_min <- select(dat, user_country, NP, topic, overall_sentiment, sentiment_confidence)

#dat_long <- pivot_longer(dat_min, cols = c('user_country', 'NP'))

dat_min%>%
  group_by(NP, user_country) %>%
  summarise(country_totals = n())
```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
